Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-27 manuscript.tex
fix biblio

also

@@

There are different solution to provide with a distance between two given spike trains. A known measure is the Victor-Purpura distance, which showed that their findings are inconsistent with Poisson models of spike trains~\citep{victor_nature_1996}. In a later study,~\citet{van_rossum_novel_2001} have defined a distance that has a time constant as a parameter. Depending on this parameter, the distance interpolates between a coincidence detector and a rate difference counter. Such distances were extended to non-Euclidean metrics and use morphological manipulations to compute spike train dissimilarity~\citet{kreuz_measuring_2007}. Mathematically, the stability of distance measures induced by level-crossing sampling can be evaluated~\citep{moser_stability_2014}, notably in light of Weyl's discrepancy measure~\citep{weyl_ber_1916} which may lead to the definition of a cross-correlation measure which is adapted to the event-based nature of spiking signals. These observations lead to the intuition that each distance may be related as the optimal solution of a generative model for these measures. % ~\citep{}

@@

Clustering and control for adaptation uncovers time-warped spike time patterns in cortical networks in vivo~\citep{Isbister} They discovered (in vivo) that the times that individual neurons spiked within a sequence depended on the excitability of the cortex when a stimulus was presented.
% dynamical models
Dumas and colleagues~\citep{panahi_generative_2021} : three levels / fourth paradigm~\citep{tolle_fourth_2011} i.e., data exploration in which the scientific models are fit to the data by learning algorithms.
Emergence of electronic architectures specialized in Sparse Event-Based Convolutions~\citep{di_mauro_alfio_sne_2022} or of sparsity aware algorithms~\citep{yin_sata_2022}.

@@

% development
scaffolding of neural assemblies / existence of critical periods :~\citep{dard_rapid_2021}

>>>>

@@

There are different solution to provide with a distance between two given spike trains. A known measure is the Victor-Purpura distance, which showed that their findings are inconsistent with Poisson models of spike trains~\citep{victor_nature_1996}. In a later study,~\citet{van_rossum_novel_2001} have defined a distance that has a time constant as a parameter. Depending on this parameter, the distance interpolates between a coincidence detector and a rate difference counter. Such distances were extended to non-Euclidean metrics and use morphological manipulations to compute spike train dissimilarity~\citet{kreuz_measuring_2007}. Mathematically, the stability of distance measures induced by level-crossing sampling can be evaluated~\citep{moser_stability_2014}, notably in light of Weyl's discrepancy measure~\citep{weyl_ueber_1916} which may lead to the definition of a cross-correlation measure which is adapted to the event-based nature of spiking signals. These observations lead to the intuition that each distance may be related as the optimal solution of a generative model for these measures. % ~\citep{}

@@

Clustering and control for adaptation uncovers time-warped spike time patterns in cortical networks in vivo~\citep{isbister_clustering_2021} They discovered (in vivo) that the times that individual neurons spiked within a sequence depended on the excitability of the cortex when a stimulus was presented.
% dynamical models
Dumas and colleagues~\citep{panahi_generative_2021} : three levels / fourth paradigm~\citep{tolle_fourth_2011} i.e., data exploration in which the scientific models are fit to the data by learning algorithms.
Emergence of electronic architectures specialized in Sparse Event-Based Convolutions~\citep{di_mauro_alfio_sne_2022} or of sparsity aware algorithms~\citep{yin_sata_2022}.

@@

% development
scaffolding of neural assemblies / existence of critical periods :~\citep{dard_rapid_2022}
